A generalized definition of multidimensional item response theory parameters

### 2024-05-28 output/paper_draft/paper_M2PLM_parameters.Rmd
Clarifies interpretation of null discrimination

In the non-cognitive domain, the use of so-called negatively-keyed items
---items that tap the negative pole of a certain trait, and thus
usually reverse-scored--- is also widespread
[consider e.g. the statement "Neglect my duties" in the Conscientiousness item
of the Big-Five Factor Markers, @noauthor_international_nodate].
It is common to find instruments that combine
positively- and negatively-keyed items.
Moreover, a complex item may have discrimination parameters with opposite signs
for different latent dimensions.<!--# Examples? -->
Take the multidimensional version of the nominal categories model
[@thissen_nominal_2010] as an example,
and consider two response categories tapping a different construct each:
A positive change in the dimension tapped by one category will inevitably
lead to a decrease in the probability of response to the other category.
One can easily note that a monotonically decreasing probability for a certain
dimension is given by a non-positive discrimination parameter
(and an unchanging probability by a null discrimination parameter),<!--# Actually, this also applies to the cognitive domain, which may not be very well explained. -->
contrary to the constraints imposed by @reckase_difficulty_1985 [p. 411].
However, the multidimensional item parameters can also be defined for
items with monotonically non-increasing probabilities, as we will see.

>>>>

In the non-cognitive domain, the use of so-called negatively-keyed items
---items that tap the negative pole of a certain trait, and thus
usually reverse-scored--- is also widespread
[consider e.g. the statement "Neglect my duties" in the Conscientiousness item
of the Big-Five Factor Markers, @noauthor_international_nodate].
It is common to find instruments that combine
positively- and negatively-keyed items.
Moreover, a complex item may have discrimination parameters with opposite signs
for different latent dimensions.<!--# Examples? -->
Take the multidimensional version of the nominal categories model
[@thissen_nominal_2010] as an example,
and consider two response categories tapping a different construct each:
A positive change in the dimension tapped by one category will inevitably
lead to a decrease in the probability of response to the other category.
One can easily note that a monotonically decreasing probability for a certain
dimension is given by a non-positive discrimination parameter
(and an unchanging probability by a null discrimination parameter,
which also applies to cognitive instruments),
contrary to the constraints imposed by @reckase_difficulty_1985 [p. 411].
However, the multidimensional item parameters can also be defined for
items with monotonically non-increasing probabilities, as we will see.
